### 2015-05-05 draft.tex
..
two column

\documentclass[11pt]{article}
\usepackage[latin1]{inputenc}

\usepackage{times}
\usepackage{latexsym}
\usepackage[bottom=20mm, top=20mm, left=20mm, right=20mm]{geometry}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{listings}
\usepackage{bussproofs}
\usepackage{comment}
\usepackage[numbers]{natbib}
\usepackage{graphicx} % Graphics support
\usepackage{caption} % Improved captions
\usepackage{subfig} % Inclusion of subfigures

@@

\section*{API and Decision Trees}
   \subsection*{Range-based Branching}
   % Why range instead of actual value, pre-generation of rules using symbolic pre-execution

@@

@@

\end{lstlisting}
\caption{Pseudocode for the compile function}
\end{figure}

@@

@@

\caption{Pseudocode for the run function}
  \end{figure}

@@

\section*{Evaluation}
% 1) optimality w.r.t. packets seen by the controler?
% 2) more examples
% 3) simulated run

>>>>

\documentclass[preprint]{sigplanconf}
\usepackage[latin1]{inputenc}
\usepackage{times}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{listings}
\usepackage{bussproofs}
\usepackage{comment}
\usepackage[numbers]{natbib}
\usepackage{graphicx} % Graphics support
\usepackage{caption} % Improved captions
\usepackage{subfig} % Inclusion of subfigures

@@

\section*{Decision Trees and Algorithmic Policies}
   \subsection*{Range-based Branching}
   % Why range instead of actual value, pre-generation of rules using symbolic pre-execution

@@

   \subsection*{Combining Algorithmic Policies}
   % cross, ``holes''

@@

\end{lstlisting}
\caption{Pseudocode for the compile function}
\label{fig:compile-pseudo}
\end{figure}

@@

We provide a function \lstinline|run| to simulate the controller policy on a sequence of packets. \lstinline|policy| is an abstract datatype solely returned by \lstinline|compile| (see Fig.~\ref{fig:compile-pseudo}). In addition to the policy, \lstinline|run| takes in a list of packets represented as list of pairs of \lstinline|field| and \lstinline|int|, representing the values of the different fields of the packet. We expect all fields to be set exactly once for each packet in the list.

\lstinline|run| starts by building the symbolic rules for the given policy, and generating the concrete rules assuming all relations to be empty. In sequence, packet are matched with the current concrete rules, recording the forwarding decision. If a packet is sent to the controller, we evaluate the policy on the packet, potentially adding or removing tuples from relations. We then re-generate the concrete rules with the updated relation, before recording the forwarding decision.

@@

\caption{Pseudocode for the run function}
\label{fig:run-pseudo}
  \end{figure}

@@

% probably no evaluation :(
\section*{Evaluation}
% 1) optimality w.r.t. packets seen by the controler?
% 2) more examples
% 3) simulated run
